Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-09 manuscript/climate_sensitivity_draft.Rmd
minor updates to analysis methods

Analyses focused on testing the predictions presented in Table 1, with $Rt$ as the response variable. The general statistical model for hypothesis testing was a generalized linear mixed model with $Rt$ as the response variable, tree nested within species as a random effect, and one or more independent variables as fixed effects. Generalized linear mixed models were implemented in the **XX** package in R [**REF**]. We used AICc to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. AICc refers to a corrected version of AICc, and is best suited for small data sizes [see @brewer_relative_2016]

Models were run for all drought years combined and for each drought year individually. In order to determine the relative importance of each predictor variable individually, we first implemented models with the variable in question as a fixed effect, along with drought year (for model with all drought years combined) and $ln[H]$ (included in null models because of it's substantial influence). Variables were considered to have significant influence on $Rt$ when AICc was reduced by $\ge$ 2.0 relative to the corresponding null model lacking that variable (Table 4).

We then determined the best full models for predicting $Rt$ for each individual drought year and for all years combined. Candidate variables were selected, based on the single-variable tests, as those that had a consistent direction of response across all droughts and whose addition to a corresponding null model improved fit (at $\Delta$AICc $\ge$ 1.0) in at least one drought year (Table 4). We note that the $\Delta$AICc $\ge$ 1.0 criterion is not a test of significance, but of whether the variable has enough influence to be considered as a *candidate* variable in full models. We compared models with all possible combinations of candidate variables and identified the full set of models within $\Delta$AICc=1 of the very top model (that with lowest AICc), henceforth referred to as "full models". When a variable appeared in all top models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction by the full models. If the variable appeared in only some of the models, we considered this partial support/rejection.

>>>>

Analyses focused on testing the predictions presented in Table 1, with $Rt$ (or $Rt_{ARIMA}$) as the response variable. Models were run for all drought years combined and for each drought year individually. 
The general statistical model for hypothesis testing was a generalized linear mixed model (GLMM), implemented  in the **XX** package in R [**REF**], with $Rt$ (or $Rt_{ARIMA}$) as the response variable, tree nested within species as a random effect, and independent variables including drought year (multi-drought model only), $ln[H]$*$TWI$, crown position, and 1-2 species traits (see below). 
We used AICc to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. 
AICc refers to a corrected version of AICc, and is best suited for small data sizes [see @brewer_relative_2016].

To avoid over-fitting models with five species traits (Table 2) across only 12 species, we did not include all traits as fixed effects in a single GLMM, but rather conducted individual tests of each species trait to determine the relative importance and appropriateness for inclusion in the main model. 
These tests followed the model structure specified above.
Trait variables were considered appropriate for inclusion in the main model if they had a consistent direction of response across all droughts and if their addition to a corresponding null model lacking the trait improved fit (at $\Delta$AICc $\ge$ 1.0) in at least one drought year (Table 4). 
We note that the $\Delta$AICc $\ge$ 1.0 criterion is not a test of significance, but of whether the variable has enough influence to be considered as a *candidate* variable in full models.

We then determined the best full models for predicting $Rt$ (or $Rt_{ARIMA}$). 
To do so, we compared models with all possible combinations of candidate variables and identified the full set of models within $\Delta$AICc=1 of the very top model (that with lowest AICc). 
When a variable appeared in all top models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction by the full models. 
If the variable appeared in only some of the models, we considered this partial support/rejection.
